Performance Evaluation of Big Data Management Strategies for Neuroinformatics

### 2018-11-22 paper.tex
Some restructuration

\title{Performance Evaluation of Big Data Management Strategies\\ for Neuroinformatics}

@@

% Big Data Engines have been developed mostly for text applications, 
%  in particular Web. Mention Spark and Dask

@@

% Make a table to explain where data locality and in-memory computing are
% available.

\subsection{Page Cache Model} % perhaps other models if relevant. 0.5 page

@@

@@

@@

% interactive gantt charts?

@@

\subsection{General concepts}

% Shared fs vs local disk vs in-memory: what do we gain?

% Can we emulate in-memory computing using write buffers or tmpfs?

% Scheduling: load balance as much as you can.
% (which isn't what nipype multiproc does)

% tmpfs and local disks fill up: need cleanup.

@@

\subsection{Engine-specific observations}

% Do we see the effect of Java serialization?

>>>>

\title{Performance Evaluation of Big Data Management Strategies for Neuroinformatics}

@@

% Big Data Engines have been developed mostly for text applications, 
%  in particular Web. Mention Spark and Dask
Big Data processing engines have been leveraging data locality, 
in-memory computing and lazy evaluation to reduce the impact of data 
manipulation on the performance of applications. From early Hadoop 
implementations~\cite{hadoop} to Apache Spark~\cite{spark} and 
Dask~\cite{dask}, these frameworks have gained popularity and are now 
becoming mainstream in data analytics.

In scientific data analysis, however, the adoption of Big Data engines

@@

\subsection{Performance Models}

\subsubsection{In-Memory File System}

\subsubsection{Local Disk (Page Caching)} % 0.5 page

@@

\subsubsection{Shared File System}

% is there a page cahe when writing to a socket? there must be!
% anyway the model is in the form of Eq 1, but now delta is the network bandwidth
% and gamma is the total number of concurrent processes.
% also, is lustre going to slow down network writes?

% Make a table to explain where data locality and in-memory computing are
% available.  As a summary of the models.

% Even if we end up not using simulation, here we should explain
% why the model in simgrid is limited. Refer to Fred's paper at CCGrid 2017.
% The following sub-sections become a set of models that we could implement
% in simulation to make it more realistic.

% Talk about ~\cite{lebre2015adding}. Most simulation toolkits have focused on task 
%  scheduling. And https://dl.acm.org/citation.cfm?id=3041715

% And Wrench.

@@

% separate this in (1) the concepts, put in the model sections below, 
% (2) the implementation 'details', put in the experiments

@@

\subsection{Model Evaluations}

\subsection{CPU Time}
% Comment on the general trend

\subsection{Image Block size}
% Comment on the general trend

\subsection{Data Size}
% Comment on the general trend

\subsection{Iterations}
% Comment on the general trend

% Interactive gantt charts?

@@

\subsection{Effect of In-Memory Computing}
% Shared fs vs local disk vs in-memory: what do we gain?

\subsection{Effect of Data Locality}

% Effect of Lazy Evaluation?

\subsection{Can \texttt{tmpfs} and Page Caches Emulate In-Memory Computing?}
% tmpfs and local disks fill up: need cleanup.
% Can we emulate in-memory computing using write buffers or tmpfs?

\subsection{Scheduling Remarks}
% Scheduling: load balance as much as you can.
% (which isn't what nipype multiproc does)

\subsection{Other Comments}

@@

\subsection{Engine-Specific Comparisons}

% Spark vs Nipype
% Do we see the effect of Java serialization?
